PRS dendrogram clusters

### 2021-11-16 notebooks/03-Fig3abde_4acd-051821.Rmd

# Load packages
```{r message=FALSE, warning=FALSE, tags=c()}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- brewer.pal(n = 12, name = "Set3")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

>>>>

# Load packages
```{r message=FALSE, warning=FALSE, tags=c()}
#library(tidyverse)
if (!require('remotes')){
install.packages('remotes', repos='http://cran.us.r-project.org')}
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- brewer.pal(n = 12, name = "Set3")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

### 2021-11-16 notebooks/09-Fig1b.Rmd

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('enm/R/plot_density_prs.R')
#source('enm/R/get.subclusters.dendrogram.R')
library(RColorBrewer)
col =brewer.pal(n=8,name='Set1')
sensor_colors = col[1:4]
effector_colors = col[5:8]
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.Enm import Enm
from enm.utils import *
import scipy.cluster.hierarchy as sch
print(os.getcwd())
with open(f'../data/interim/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))

@@

```{python}
prs_mat = e_pcc.prs_mat
quantile_threshold =  0.95
method = 'ward'
metric = 'seuclidean'
q99 = np.quantile(prs_mat, quantile_threshold)
prs_mat_cl = copy.deepcopy(prs_mat)
prs_mat_cl[prs_mat_cl > q99] = q99
prs_mat_cl_orig = prs_mat_cl
# , optimal_ordering=True)
#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
# ,optimal_ordering=True)
#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)

row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
#use_condaenv('enm')
#setwd('../')
library(RColorBrewer)
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import os
from enm.Enm import Enm
from enm.utils import *
import scipy.cluster.hierarchy as sch
with open(f'data/interim/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))

@@

```{python}
prs_mat = e_pcc.prs_mat
quantile_threshold =  0.95
method = 'ward'
metric = 'seuclidean'
q99 = np.quantile(prs_mat, quantile_threshold)
prs_mat_cl = copy.deepcopy(prs_mat)
prs_mat_cl[prs_mat_cl > q99] = q99
prs_mat_cl_orig = prs_mat_cl
row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)
